An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-23 poly-embed-journal/poly-embed-journal.tex
Pre meeting/lunch push.  Rounding out a few more claims that lead to the actual lemma result

  $\implies$ 
  Fix any $x \in \reals^\Y_+$.
  $x \in \H_\Y$ by previous Claim \jessie{ref}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.

@@

\begin{claim}
	$\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Theta \subseteq \{\Gamma_r \mid r \in \R'\}$.
\end{claim}

\begin{claim}
	$\Theta$ is exactly equal to $\{\Gamma_r \mid r \in \R^*\}$ \jessie{Not sure if this is it.}
\end{claim}

\begin{claim}
	For any $r \in \R$ with $v = L(r)$, we have $\Gamma_r \subset \theta(v)$. \jessie{=?}
\end{claim}

>>>>

  $\implies$ 
  Fix any $x \in \reals^\Y_+$.
  $(x,c) \in \H_\Y$ for all $c \in \reals$ by previous Claim \jessie{ref}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.

@@

\begin{claim}
	For any $r \in \R$, take $v \in \V$ such that $v = L(r)$.
	$\theta(v) = \Gamma_r$.
\end{claim}
\begin{proof}
	\begin{align*}
	p \in \theta(v) &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
	&\iff v \in \argmin_{v' \in \V} \inprod{v'}{p}\\
	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\ 
	&\iff p \in \Gamma_r
	\end{align*}
\end{proof}

\begin{claim}
	$\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Theta \subseteq \{\Gamma_r \mid r \in \R'\}$.
\end{claim}
\begin{proof}
	\jessie{Ran out of time but mild speedbump to show the forward implication.  Reverse is in my notebook.}
\end{proof}

\jessie{Don't think this claim is actually necessary?}
\begin{claim}
	$\Theta = \{\Gamma_r \mid r \in \R^*\}$ 
\end{claim}
\begin{proof}
	Fix $v \in \V^*$.
	By Corollary 9, there is some $r \in \R^*$ so that $v = L(r)$.
	\begin{align*}
	\theta(v) \in \Theta &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\
	&\iff r \in \argmin_{r' \in \R^*} \inprod{L(r')}{p}\\
	&\iff r \in \Gamma_r
	\end{align*}
\end{proof}

\jessie{(7)}
\begin{claim}
	For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.
\end{claim}
\begin{proof}
	Let $v = L(r) \in \V$.
	By Claim 14\jessie{ref}, face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
	We must then have $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*}) \cap \simplex$, which is precisely defined as $\theta(v) \subseteq \theta(v^*)$.
	Since $v = L(r)$, this can be re-written $\theta(v) = \Gamma_r$ by Claim 17.
	The result then follows $\Gamma_r \subseteq \theta(v^*)$.
\end{proof}
